Baseline centering problem

### 2018-12-13 paper/tangotd.tex

\paragraph{A learned representation for $\Delta^{-1}$.} $\Delta^{-1}$
contains all the necessary to do policy gradient or actor-critic with
arbitrary reward functions, as seen above. It is feasible to store a
compact and useful representation of $\Delta^{-1}$? Ideally, such a
representation should be learned from the \emph{two-sided} Bellman
equations
\begin{equation}
\label{eq:greenbell}
\Delta^{-1}=\Id + P \Delta^{-1},\qquad \Delta^{-1}=\Id + \Delta^{-1}P
\end{equation}
which represent that, when observing a transition $s\to s'$, we update
both the ways to arrive at $s'$ and the ways to start at $s$.

>>>>

\paragraph{A learned representation for $\Delta^{-1}$.} $\Delta^{-1}$
contains all the necessary to do policy gradient or actor-critic with
arbitrary reward functions, as seen above. It is feasible to store a
compact and useful representation of $\Delta^{-1}$? Ideally, such a
representation should be learned from the \emph{two-sided} Bellman
equations
\begin{equation}
\label{eq:greenbell}
\Delta^{-1}=\Id + P \Delta^{-1},\qquad \Delta^{-1}=\Id + \Delta^{-1}P
\end{equation}
With these two equations, when observing a transition $s\to s'$, we update
both the model of what happens when we start at $s$ (left equation,
standard Bellman), and the model of how to arrive at $s'$ (right
equation, rarely used as far as I know).
